The Astropy Project

### 2017-12-11 registry.tex
remove the overly-complicated table formatting and just put it in the table specification directly

\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs} \\

>>>>

\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther & \citealt{marxs} \\
